Organization

### 2024-02-24 Misc/data_organize.qmd
create e3 ds

>>>>

d <- readRDS(here::here("data/e3_08-21-23.rds"))
levels(d$condit)
dtest <- d %>% filter(expMode %in% c("test-Nf","test-train-nf")) %>% group_by(id,lowBound) %>% 
  mutate(nBand=n(),band=bandInt,id=factor(id)) %>% group_by(id) %>% mutate(nd=n_distinct(lowBound))
dtest <- dtest %>% group_by(id,lowBound) %>% filter(nBand>=5 & nd==6)
dtest <- dtest %>% group_by(id) %>% filter(!id %in% unique(dtest$id[dtest$nBand<5]))

#saveRDS(ds,here::here("data/e3_md_02-23-24.rds"))
